
\chapter*{General introduction  \markboth {General introduction}{}}
%\markboth {General introduction}{}}
%\addcontentsline{toc}{chapter}{General introduction}

\lettrine[lines=2]{W}\\aikatōhea is a Māori tribe of the eastern Bay of Plenty region in New Zealand, known for their rich cultural heritage, deep connection to the land and sea, and their ongoing efforts to promote the sustainable management of natural resources for future generations \autocite{Whakatoh65:online}.

\paragraph*{}

The goal of this report is to introduce how we start the work to make traditional books more accessible to young generations. 
These books are an important part of the iwi's cultural and historical identity and contain valuable information about their way of life, customs, and beliefs.

\paragraph*{}

To achieve this goal, the Waikatōhea iwi has decided to scan their traditional books and convert them into eBooks format. 
This will make it easier for young members of the tribe to access these books and learn about their heritage. 
The books will be made available on a dedicated online platform, which will also serve as a space for sharing and exchanging knowledge and ideas about the tribe's culture and history.

\paragraph*{}

The platform will allow users to read the books, share their thoughts and opinions, and interact with other members of the tribe. 
It will also provide a space for non-members to learn about the Waikatōhea iwi and their culture. 
The platform will be open to anyone who is interested in learning about the tribe's culture and history. 
At the same time, it will serve as a way for members of the tribe from different locations to connect and learn from each other.

\paragraph*{}

To achieve this goal, the group 1 has conducted extensive research into various online platforms available on the market. 
We have identified key features and content formats of successful platforms and hope to incorporate them into our own platform in order to meet the specific needs of the tribe and project.